### 2018-05-01 manuscript.rmd
updated poisson chains and stats about runs

@@

ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution, and bootstrap values were estimated using `r length(bootstrap_trees)` replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and eight independent MCMC chains were run under the CAT-Poisson model. The BI analyses did not converge (CAT-Poisson: maxdiff=1, meandiff=0.0148; CAT-GTR: maxdiff=1, meandiff=0.0221709). Only the results from the CAT-Poisson model are presented here. Two chains (chain1 and chain3) did not burn in after 1405 and 4695 iterations and were excluded from the analyses. Visual inspection of the traces indicated that a burn in of `r burn_in` trees was sufficient for all CAT-Poisson runs. This left `r length( phylobayes_trees )` trees in the posterior.

@@

```{r supplementary trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution. Unlabeled nodes have support >0.99. A. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8133157.335; AIC:16266530.7277.  B. JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories. Likelihood:-8113694.922; AIC: . C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8156043.772; AIC score: 16312303.6120 "}

>>>>

	#remove two chains that are stuck in local maxima
	input_files_phylobayes= input_files_phylobayes[-which(input_files_phylobayes %in% c("chain1_trimmed60_poisson.treelist","chain3_trimmed60_poisson.treelist"))]

@@

ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution, and bootstrap values were estimated using `r length(bootstrap_trees)` replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and eight independent MCMC chains were run under the CAT-Poisson model. The BI analyses did not converge (CAT-Poisson: maxdiff=1, meandiff=0.0185032; CAT-GTR: maxdiff=1, meandiff=0.045415). Only the results from the CAT-Poisson model are presented here. Two chains (chain1 and chain3) were stuck in local maxima after 1405 and 4695 iterations and were excluded from the analyses. Visual inspection of the traces indicated that a burn in of `r burn_in` trees was sufficient for all CAT-Poisson runs. This left `r length( phylobayes_trees )` trees in the posterior.

@@

```{r supplementary trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution. Unlabeled nodes have support >0.99. A. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8133157.335; AIC:16266530.7277.  B. JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories. Likelihood:-8113694.922; AIC:16227609.9565 . C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8156043.772; AIC score: 16312303.6120 "}
